Conversations in Time: Interactive Visualization to Explore Structured Temporal Data

### 2021-07-28 rjdistill_version/tsibbletalk.Rmd
Rmd reworked to fit new format

---
title: "Conversations in time: interactive visualization to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address: Department of Statistics
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address: Department of Econometrics and Business Statistics
  email: dicook@monash.edu
bibliography: tsibbletalk.bib
abstract: >
  Temporal data often has a hierarchical structure, defined by categorical variables describing different levels, such as political regions or sales products. The nesting of categorical variables produces a hierarchical structure. The \CRANpkg{tsibbletalk} package is developed to allow a user to interactively explore temporal data, relative to the nested or crossed structures. It can help to discover differences between category levels, and uncover interesting periodic or aperiodic slices. The package implements a shared `tsibble` object that allows for linked brushing between coordinated views, and a shiny module that aids in wrapping timelines for seasonal patterns. The tools are demonstrated using two data examples: domestic tourism in Australia and pedestrian traffic in Melbourne.
preamble: |
  \usepackage{subfig}
output: rticles::rjournal_article
---

>>>>

---
title: "Conversations in Time: Interactive Visualization to Explore Structured Temporal Data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address: Department of Statistics
  email: earo.wang@auckland.ac.nz
  orcid: 0000-0001-6448-5260
- name: Dianne Cook
  affiliation: Monash University
  address: Department of Econometrics and Business Statistics
  email: dicook@monash.edu
  orcid: 0000-0002-3813-7155
date: "`r Sys.Date()`"
abstract: >
  Temporal data often has a hierarchical structure, defined by categorical variables describing different levels, such as political regions or sales products. The nesting of categorical variables produces a hierarchical structure. The \CRANpkg{tsibbletalk} package is developed to allow a user to interactively explore temporal data, relative to the nested or crossed structures. It can help to discover differences between category levels, and uncover interesting periodic or aperiodic slices. The package implements a shared `tsibble` object that allows for linked brushing between coordinated views, and a shiny module that aids in wrapping timelines for seasonal patterns. The tools are demonstrated using two data examples: domestic tourism in Australia and pedestrian traffic in Melbourne.
preamble: |
  \usepackage{subfig}
creative_commons: CC BY
output: 
  - rjtools::rjournal_web_article
  - rjtools::rjournal_pdf_article
# per R journal requirement, the bib filename should be the same as the output 
# tex file. Don't forget to rename the bib file and change this example value.
bibliography: tsibbletalk.bib
---
